### 2021-03-04 introduction.tex
minor review

Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
The authors argue that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often
assume that additional behaviors are possible than actually would be.
%\kn{Ok. In the first paragraph we discuss static analysis in general to detect vulnerabilities and now without mentioning it prior we seem to mention static analysis can also mine sandboxes. The overall flow of definitions needs some thought}
Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime. In addition,
code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features}
of programming languages are often used to introduce malicious behavior. Even though these claims
seem reasonable, Jamrozik et al. do not present an empirical validation about the limitations of static analysis to mine sandboxes.
Consequently, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.

@@

Our goal in this paper is to understand how static analysis
algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. To this end, we performed two studies. In the
first, we conduct a replication of the \blls. Our research differs from the original work in three aspects: (a)
we isolate the effect of the static analysis component of DroidFax, (b) we consider in our study more recent dynamic analysis tools for testing Android apps,
and (c) we extend the execution time and the number of executions of each test case generator tool for all apps
in our dataset. In the second study, we leverage FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} to understand how a more advanced static analysis approach
(based on taint analysis) can complement dynamic analysis in the task of mining sandboxes.

Here we also use DroidXP to integrate different dynamic analysis tools and then build a
general understanding about the use of dynamic and static analysis tools for mining
Android sandboxes. Although we presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
here we discuss the results of a broader investigation
that uses DroidXP to explains the performance of static and dynamic analysis
approaches for mining sandboxes.

>>>>

Jamrozik et al.~\cite{DBLP:conf/icse/JamrozikSZ16} argue in favor of dynamic analysis for mining sandboxes, instead of using static analysis.
The authors state that dynamic analysis exceeds static analysis on mining Android sandboxes because the analysis must often
assume that additional behaviors are possible than actually would be.
%\kn{Ok. In the first paragraph we discuss static analysis in general to detect vulnerabilities and now without mentioning it prior we seem to mention static analysis can also mine sandboxes. The overall flow of definitions needs some thought}
Otherwise, static analysis might determine that some behavior is impossible and therefore no longer needs to be checked at runtime. In addition,
code that uses dynamic features (such as reflection) poses additional challenges to static analysis algorithms---even though \emph{dynamic features}
of programming languages are often used to introduce malicious behavior. Even though these claims
seem reasonable, previous research do not present empirical assessments about the limitations of static analysis to mine sandboxes.
Consequently, it is not clear whether and how both approaches (dynamic and static analysis) could complement each other in the process of mining Android sandboxes.

@@

Our goal in this paper is to understand how static analysis
algorithms might complement dynamic analysis approaches in the process of mining Android sandboxes. Here we
present the results of two empirical studies that aim to
address our research goal. In the
first study, we conduct a replication of the \blls, though our research differs from the original work in three aspects: (a)
we isolate the effect of the static analysis component of DroidFax, (b) we included a recent dynamic analysis tool for testing Android apps,
and (c) we extend the execution time and the number of executions of each test case generator tool for all apps
in our dataset. Differently, in the second study we explore how a more advanced static analysis approach
(based on taint analysis) can complement dynamic analysis in the task of mining sandboxes---using
the FlowDroid~\cite{DBLP:conf/pldi/ArztRFBBKTOM14} infrastructure for analysing Android apps.

We presented and evaluated DroidXP in a conference paper~\cite{DBLP:conf/scam/CostaMCMVBC20},
and here we discuss the results of a broader investigation
that also uses DroidXP to explains the performance of static and dynamic analysis
approaches for mining sandboxes.
